---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rtwitter

```{r eval=FALSE, include=FALSE}
#this part normally should be outside of the code chunk:
<!-- badges: start -->
  [![R-CMD-check](https://github.com/selimyaman/Rtwitter/workflows/R-CMD-check/badge.svg)](https://github.com/selimyaman/Rtwitter/actions)
<!-- badges: end -->
  
# this is the code to renew readme file
  devtools::build_readme()
```

Rtwitter lets you analyze and visualize Twitter data. You can easily do a sentiment analysis, plot interactive word networks, or create table of most used emojis along with 13 other functions for various visualization purposes.

The package is still in its early versions - but eventually it will transform into an Rshiny application where you can type a keyword and see various analytics. Around those times, I plan to publish it in CRAN as well.

## Installation

You can install the development version of Rtwitter from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("selimyaman/Rtwitter")
```

## Example Usage

```{r eval=FALSE}
library(Rtwitter)

# get the example dataset on Ukraine tweets
tweets <- Rtwitter::tw 

# visualize word associations
Rtwitter::word.network(tweets)
```

You can check out other functions included in the package by typing `Rtwitter::` in your console.
